\textbf{Honeypot Assignment: \\ \emph{Group Contagiarium}}

### 2012-01-10 Paper_honeypot.tex
Verdere aanpassingen

The first service we will be talking about is Kippo. During the interaction phase we've had 2610 login attempt on our Kippo client and 3871 connections. 54 of these attempts were succesfull.
We have made a top 5 of most tried usernames in these login attempts:

@@

It is not entirely unexpected that the username "root" is tried most ofted. 
We assume the username "w000t" is a backdoor user created in one or more exploits.
Interesting to note is that "jenny" is the name of a fake employee listed on the our honeypot website.
Most usernames were tried multiple times, even if they made no sense to us for instance msnayeem\_iitd tried to log in four times.

@@

An interesting situation was someone that tried to log in to the honeypot with the user root, just trying a list of years (1960-1980). He obviously thought we would use a birthyear as our password (which was not the case).

@@

Also serveral client IDs are visible in these logs:

\begin{itemize}
\item ``\emph{``-''}'' (3432 attempts)

This is a blank user/client ID.

@@

\tocheck{Info over MiRRORS}

@@

The attackers using ``ZmEu'' found one valid path: /phpmyadmin/, however he did not exploit this. It is interesting to see that both several ``\emph{''-''}'' and several ``ZmEu'' users are scanning for ``/w00tw00t.at.blackhats.romanian.anti-sec:)'' and ``/w00tw00t.at.ISC.SANS.DFind:)''

@@

``Morfeus Fucking Scanner'' was used by one attacker, that soly searched for /user/soapCaller.bs. We could not find anything on this .bs file.
\end{itemize}

We expected to see several occurances of ``/robots.txt'' because this is a common way to start when using a search engine crawler, but none were found.

@@

\begin{itemize}
\item Low/High interaction phase
\item GHH
\item etc
\end{itemize}

>>>>

The first service we will be talking about is Kippo. During the interaction phase we've had 2610 login attempt on our Kippo client and 3871 connections. 54 of these attempts were successful.
We have made a top 5 of most tried usernames in these login attempts:

@@

It is not entirely unexpected that the username ``root'' is tried most often. 
The username ``w000t'' is a backdoor user created in the FAKE Apache 2.2.17 exploit.
Interesting to note is that ``jenny'' is the name of a fake employee listed on the our honeypot website.
Most usernames were tried multiple times, even if they made no sense to us for instance ``msnayeem\_iitd'' tried to log in four times.

@@

An interesting situation was someone that tried to log in to the honeypot with the user root, just trying a list of years (1960-1980). It seems like an unusual brute force attack. Assuming someone used their birthday as a password, which still happens a lot, it is unlikely that this someone just used their birth year and not the whole birthday. However brute forcing for the entire birthday takes way to long. So for a quick and easy brute force it is unlikely to yield results.

@@

Also several client IDs are visible in these logs:

\begin{itemize}
\item \emph{``-''} (3432 attempts)

This is a blank user/client ID. Which seems to be a popular client to use when you want to find weak software on a server.

@@

Due to the well-chosen name we could not find additional information on this client. Mirrors is a frequently used word on the internet.

@@

The attackers using ``ZmEu'' found one valid path: /phpmyadmin/, however he did not exploit this. 
It is interesting to see that both several \emph{''-''} and several ``ZmEu'' users are scanning for ``/w00tw00t.at.blackhats.romanian.anti-sec:)'' and ``/w00tw00t.at.ISC.SANS.DFind:)''

@@

``Morfeus Fucking Scanner'' was used by one attacker, that solely searched for /user/soapCaller.bs. We could not find anything on this .bs file.
\end{itemize}

We expected to see several occurrences of ``/robots.txt'' because this is a common way to start when using a search engine crawler, but none were found.

@@
